Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2021-09-27 methods_paper/fabl-paper.tex
updates.

@@

\textcolor{blue}{Define \(m^{f\ell}:= P(\Gamma_{ij}^f = l |Z_j = i)\) as  the probability of a match having level $\ell$ of disagreement for feature $f.$ Define \(u^{f\ell}:= P(\gamma_{ij}^f = l |Z_j \neq i)\) as the corresponding probability for non-matches. Next, we adopt Fellegi and Sunter's conditionally independent fields assumption
that the level of agreement on one feature is independent of the level of
agreement on another.\footnote{Though this assumption is often not reasonable
(for example, two individuals of a different genders are more likely to have different names than two individuals of the same gender),
but it is common within the record linkage literature and generally
leads to models that perform well in practice; see discussion for
further remarks.} Denote \(\lambda\) to be the (marginal)
probability that some record \(j \in \bm{X}_2\) has a match in \(\bm{X}_1\)}

@@

%\[P(\Gamma|\mathbf{Z}, \mathbf{m}, \mathbf{u}, \lambda) =\prod_{j=1}^{n_B}  \prod_{i=1}^{n_A}\mathbf{m}_{ij}^{\mathbf{1}_{z_j = i}}\mathbf{u}_{ij}^{\mathbf{1}_{z_j \neq i}}\]

@@

@@

Here the reader should the relationship between our proposed model and
that of Sadinle 2017. In his model, Sadinle constructs a prior
distribution on the entire \(\mathbf{Z}\) vector, which induces a Gibbs
sampler that strictly enforces one-to-one matching. In particular, this
sampler removes previously matches records from the set of candidate
records when sampling \(Z_j\), creating a dependency that makes the
sampler \emph{inherently serial}. We however use independent priors for
each \(Z_j\), creating a sampler that is \emph{perfectly parallelizable}, allowing for significant computational gains. More
importantly, since only the agreement pattern of \(Z_j\) is used for
calculations within the Gibbs sampler, and not the particular record
label, we can conduct this sampling only at the level of the unique
agreement patterns, offering even more computational savings. In doing
so however, we thereby weaken the one-to-one requirement from
\texttt{BRL}; our sampler does ensure that each record in \(B\) can be
matched to at most one record in \(A\), but allows for the possibility
that multiple records in \(B\) match to the same record in \(A\). We then resolve these contradictions through a straightfoward post-processing step. We
explore the ramifications of this distinction with the El Salvador case
study.

>>>>

\subsection{Generalized Beta Linkage Model}
In this section, our model can be written as a Bayesian model for comparison data. In general, it has the same form of \cite{sadinle_bayesian_2017} and can be written as follows:

\begin{align}
&\bm{\Gamma}_{ij} \mid Z_j =i \stackrel{iid}{\sim} \mathcal{M}(\bm{m})  \\
&\bm{\Gamma}_{ij} \mid Z_j \neq i \stackrel{iid}{\sim} \mathcal{U}(\bm{u}) \notag \\
& \bm{Z} \sim \mathcal{B}, \notag
\end{align}
where $\mathcal{B}$ represents a prior on the space of bipartite matchings. $\mathcal{M}(\bm{m})$ and $\mathcal{M}(\bm{u})$ are models for the comparison vectors of matches and non-matches.

@@

\textcolor{blue}{Define \(m^{f\ell}:= P(\Gamma_{ij}^f = l |Z_j = i)\) as  the probability of a match having level $\ell$ of disagreement for feature $f.$ Define \(u^{f\ell}:= P(\gamma_{ij}^f = l |Z_j \neq i)\) as the corresponding probability for non-matches. Next, we adopt Fellegi and Sunter's conditionally independent fields assumption
that the level of agreement on one feature is independent of the level of
agreement on another.\footnote{Though this assumption is often not reasonable
(for example, two individuals of a different genders are more likely to have different names than two individuals of the same gender),
but it is common within the record linkage literature and generally
leads to models that perform well in practice; see discussion for
further remarks.} Denote \(\lambda\) to be the (marginal)
probability that some record \(j \in \bm{X}_2\) has a match in \(\bm{X}_1\). In addition, denote $\bm{m}_f = (m_{f1}, \ldots, m_{fL_f})$, $\bm{u}_f = (u_{f1}, \ldots, u_{fL_f})$, 
$\bm{m}= (m_1, \ldots m_F)$, $\bm{u}= (u_1, \ldots u_F)$, and $\Phi = (\bm{m}, \bm{u})$}.

@@

@@

\textcolor{red}{It seems to me that this should be $P(\bm{Z}, \Phi \mid \bm{\Gamma})$ above and not what is currently written. }

@@

\begin{remark}
There is a clear relationship between our proposed model and that of \cite{sadinle_bayesian_2017}. 
\cite{sadinle_bayesian_2017} constructs a prior distribution on the entire \(\mathbf{Z}\) vector, 
which induces a Gibbs
sampler that strictly enforces one-to-one matching. In particular, this
sampler removes previously matches records from the set of candidate
records when sampling \(Z_j\), creating a dependency that makes the
sampler \emph{inherently serial}. On the other hand, we propose 
 independent priors for
each \(Z_j\), creating a sampler that is \emph{embarassingly parallel}, allowing for significant computational gains. 
More importantly, since only the agreement pattern of \(Z_j\) is used for
calculations within the Gibbs sampler, and not the particular record
label, this sampling is only needed at the level of the unique agreement patterns, which offers additional computational savings.  In doing so however, we thereby weaken the one-to-one requirement from
\texttt{BRL}; our sampler does ensure that each record in \(\bm{X}_2\) can be
matched to at most one record in \(\bm{X}_1\), but allows for the possibility
that multiple records in \(\bm{X}_2\) match to the same record in \(\bm{X}_1\). We resolve contradictions via a post-processing step \textcolor{red}{state what the post-processing step is Brian}. 
\end{remark}
